GPU-friendly Stroke Expansion

### 2024-04-28 paper.tex
address comments
fix figure formatting and clipped text
Tweak color of evolutes
Make the evolute segment more visible by using a brighter color.

An immediate consequence is that flattening an Euler spiral by choosing subdivision points $s_i = a\cdot i^\frac{2}{3}$ produces a near-optimal flattening, as can visually be seen in Figure\ref{fig:es_flatten}.

@@

The subdivision density for the parallel curve of an Euler spiral, normalized so that its inflection point is at -1 and the cusp of the parallel curve is at 1, is simply $1 - \sqrt{|1-s^2|}$. This function is plotted in Figure\ref{fig:subdiv_density}.

>>>>

An immediate consequence is that flattening an Euler spiral by choosing subdivision points $s_i = a\cdot i^\frac{2}{3}$ produces a near-optimal flattening, as can visually be seen in Figure~\ref{fig:es_flatten}.

@@

The subdivision density for the parallel curve of an Euler spiral, normalized so that its inflection point is at -1 and the cusp of the parallel curve is at 1, is simply $1 - \sqrt{|1-s^2|}$. This function is plotted in Figure~\ref{fig:subdiv_density}.
